---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# velo
velo is an R package which provides bicycle-related calculations frequently used by bike enthusiasts. Until now many of these functions are spread over the web, are unreliable mostly due to insufficient documentation and/or do not exist.
The main goals of the velo-package are:

* Bring together the most important bicycle-related calculations in a well-documented, transparent and reproducible manner (well, so far, there are just two functions, ...).

* In the future, RShiny should make the implemented functions interactively usable.

You can install the latest development version from github with

```{r, eval = FALSE}
if (packageVersion("devtools") < 1.6) {
    install.packages("devtools")    
    }
if (!"lazyeval" %in% installed.packages()[, "Package"]) {
devtools::install_github("hadley/lazyeval")  
}
devtools::install_github("jannes-m/velo")
```

## TO DO
- function to calculate the spoke length
- function to calculate the chain length
- implement functions in RShiny