---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# velo
**velo** is an R package which provides bicycle-related calculations frequently used by bike enthusiasts. 
So far many of these functions are spread over the web.
These are often unreliable and/or intransparent mostly due to insufficient documentation.
The main goals of the velo-package are:

* Bring together the most important bicycle-related calculations in a well-documented, transparent and reproducible manner. So far, **velo** lets you compute:
  1. chain lengths.
  1. the optimal combination of teeths for fixie bikes.
  1. spoke lenghts.
  1. the trail.

* Make them interactively usable via RShiny Apps (see the sibling [velo_apps](https://github.com/jannes-m/velo_apps) repository).

You can install the latest development version from github with

```{r, eval = FALSE}
if (packageVersion("devtools") < 1.6) {
    install.packages("devtools")    
    }
if (!"lazyeval" %in% installed.packages()[, "Package"]) {
devtools::install_github("hadley/lazyeval")  
}
devtools::install_github("jannes-m/velo")
```

## TO DO
- function calc_chain also for fixie bikes.
- build Shiny apps for all functions.
